---
editor_options: 
  markdown: 
    wrap: 72
---

# Metadata

    Course:  DS 5100
    Module:  11 R Programming 1
    Topic:   HW 11 Computing Payoff for a Quota Structure
    Author:  R.C. Alvarado (adapted)
    Date:    06 July 2022

# Student Metata

    Name:
    UVA ID:

# Instructions

A salesperson at a large tech firm is faced with a new payment
structure.

This salesperson has a quarterly quota of \$225,000.

The payment received follows a progressive schedule with four brackets
as follows:

1.  For the first 40% of quota, the salesperson receives 7% on quota
    reached
2.  For the next 30% of quota, the salesperson receives 10% on quota
    reached
3.  For the next 20% of quota, the salesperson receives 13% on quota
    reached
4.  For the next 10% of quota, the salesperson receives 16% on quota
    reached

For example, if the salesperson is 50% to quota, reaching \$112,500 of
sales, then:

-   `a` = the first 40% is paid out at 7% (payout = \$225,000 \* 40% \*
    7%)
-   `b` = the next 10% is paid out at 10%

The total payout to the salesperson would be `a + b`.

Notice what does NOT happen: getting to the second bracket does NOT mean
the payout is \$225,000 \* 50% \* 10%.

This schedule represents earnings up to 100% of quota.

We ignore sales above 100% here.

Given this, the salesperson would like to know how much she would earn
if she reaches a given percentage of quarterly quota.

Note: The quota structure in this assignment is analogous to how the US
tax system works: There are several **brackets** with rate i applied to
dollars in bracket i.

**TOTAL POINTS: 12**

# Task 1

(8 points for a function that returns the correct value.)

Write a function to these specifications:

1.  Takes input: quarterly quota (`225000`)
2.  Takes input: fraction of quarterly quota reached (`0.8` means 80%)
3.  Returns the dollar amount earned.

Call this function and print the dollar amount earned for argument 2 in
increments of 10% in a range between 0% to 100% earned.

Hint: Use `if` statements to help compute amounts in each bracket.

```{r}
# CODE HERE
```

# Task 2

(2 points for a correct graph)

Plot the amounts earned (y-axis) versus quarterly quota reached
(x-axis).

```{r}
# CODE HERE
```

# Submission

When finished, convert your code into a PDF and submit to Gradescope.

Note: You can use an R Notebook for your work, but since you have not
been taught to use them yet, you can use Jupyter on Rivanna to present
your work. Remember to choose the R kernel when starting it.
