---
title: "M11 Exercises"
author: "R.C. Alvarado"
date: '2022-07-05'
output: slidy_presentation
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

## Exercise 11.1

Write an R program to get the first 10 Fibonacci numbers.

## Solution 11.1

```{r}
Fibonacci <- numeric(10)
Fibonacci[1] <- Fibonacci[2] <- 1
for (i in 3:10) Fibonacci[i] <- Fibonacci[i - 2] + Fibonacci[i - 1]
print("First 10 Fibonacci numbers:")
print(Fibonacci)
```

## Exercise 11.2

Convert the previous code into a function. 

Instead of printing the results, just return the vector.

## Solution 11.2

```{r}

fibonacci <- function(n=10) {
  Fibonacci <- numeric(n)
  Fibonacci[1] <- Fibonacci[2] <- 1
  for (i in 3:n) Fibonacci[i] <- Fibonacci[i - 2] + Fibonacci[i - 1]
  return(Fibonacci)
}

fibonacci(20)
```
## Exercise 11.3

Write a function that takes a numeric `x` and returns 1 if 0 <= `x` <= 1, else returns 0.

Hint: use && for "and"

## Solution 11.3

```{r}
in_unit_interval <- function(x) { 
  if (x >= 0 && x <= 1) { 
    return(1) 
  }
  else { 
    return(0) 
  } 
}
```

## Exercise 11.4

Test the function on some values

## Solution 11.4

```{r}
in_unit_interval(-1) 
in_unit_interval(0) 
in_unit_interval(0.5)
in_unit_interval(1) 
in_unit_interval(2)
```

## Exercise 11.5

Write an R program to extract first 10 english letters in lower case and last 10 letters in upper case and extract letters between 22nd to 24th letters in upper case.

Hint: R comes with `letters` and `LETTERS`, two vectors that contain what you think they do.

## Solution 11.5

```{r}
print("First 10 letters in lower case:")
t = head(letters, 10)
print(t)
print("Last 10 letters in upper case:")
t = tail(LETTERS, 10)
print(t)
print("Letters between 22nd to 24th letters in upper case:")
e = tail(LETTERS[22:24])
print(e)
```

## Exercise 11.6

Write an R program to print the numbers from 1 to 100 and print "Fizz" for multiples of 3, print "Buzz" for multiples of 5, and print "FizzBuzz" for multiples of both.

## Solution 11.6

```{r}
for (n in 1:100) {
 if (n %% 3 == 0 & n %% 5 == 0) {print("FizzBuzz")}
 else if (n %% 3 == 0) {print("Fizz")}
 else if (n %% 5 == 0) {print("Buzz")}
 else print(n)
}
```

## Exercise 11.7

Write an R program to get the unique elements of a given string and unique numbers of vector.

Hint: use the `unique()` function.

## Solution 11.7

```{r}
str1 = "The quick brown fox jumps over the lazy dog."
print("Original vector(string)")
print(str1)
print("Unique elements of the said vector:")
print(unique(tolower(str1)))
nums = c(1, 2, 2, 3, 4, 4, 5, 6)
print("Original vector(number)")
print(nums)
print("Unique elements of the said vector:")
print(unique(nums))
```

## Exercise 11.8

Write an R program to find the maximum and the minimum value of a given vector.

Hint: use the `max()` and `min()` functions.

## Solution 11.8

```{r}
nums = c(10, 20, 30, 40, 50, 60)
print('Original vector:')
print(nums)   
print(paste("Maximum value of the said vector:",max(nums)))
print(paste("Minimum value of the said vector:",min(nums)))
```

## Exercise 11.9

Write an R program to create a sequence of numbers from 20 to 50 and find the mean of numbers from 20 to 60 and sum of numbers from 51 to 91.

Hint: Use `seq()`, `mean()`, and `sum()`.

## Solution 11.9

```{r}
print("Sequence of numbers from 20 to 50:")
print(seq(20,50))
print("Mean of numbers from 20 to 60:")
print(mean(20:60))
print("Sum of numbers from 51 to 91:")
print(sum(51:91))
```

## Exercise 11.10

Write a R program to create a data frame from four given vectors.

## Solution 11.10
```{r}
name = c('Anastasia', 'Dima', 'Katherine', 'James', 'Emily', 'Michael', 'Matthew', 'Laura', 'Kevin', 'Jonas')
score = c(12.5, 9, 16.5, 12, 9, 20, 14.5, 13.5, 8, 19)
attempts = c(1, 3, 2, 3, 2, 3, 1, 1, 2, 1)
qualify = c('yes', 'no', 'yes', 'no', 'no', 'yes', 'yes', 'no', 'no', 'yes')
print("Original data frame:")
print(name)
print(score)
print(attempts)
print(qualify)
df = data.frame(name, score, attempts, qualify)  
print(df)
```

## Exercise 11.11

Write a R program to extract 3rd and 5th rows with 1st and 3rd columns from the built in `airquality` data frame.

## Solution 11.11
```{r}
airquality
```
Extract 3rd and 5th rows with 1st and 3rd columns:

```{r}
airquality[c(3,5), c(1,3)]
```